ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-21 pyked.tex
Another usage example idea
First parts of PyKED section

\begin{minted}{yaml}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 10
    ...
\end{minted}

%====================================================================
\section{PyKED Architecture}
%
\todo[inline]{Bryan to do}

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}
\todo[inline]{Idea: CONV simulations using Cantera in a loop with conditions
from the Pandas output for butanol?}

>>>>

\begin{minted}{yaml}
datapoints:
  - temperature:
      - 1100 kelvin
      - uncertainty-type: absolute
        uncertainty: 10 kelvin
    ignition-delay:
      - 10 us
      - uncertainty-type: relative
        uncertainty: 0.1
    ...
\end{minted}

%====================================================================
\section{PyKED Architecture}
%
\pk{} is a Python package that currently provides the reference implementation
of the interface to \ck{} files. \pk{} reads \ck{} files, validates their
structure and content, and allows the user to interact with the datapoints
contained in the \ck{} file.

The basic user interface to the \ck{} file in \pk{} is through the
\python|ChemKED| class. The \python|ChemKED| class constructor takes the file
name of a \ck{} file or a Python dictionary containing the contents of a \ck{}
file as its argument. When the file or dictionary is loaded, it is validated to
have the correct format by Cerberus \autocite{cerberus}. The fields of the \ck{}
file are stored as instance attributes of the \python|ChemKED| class.

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}
\todo[inline]{Idea: CONV simulations using Cantera in a loop with conditions
from the Pandas output for butanol?}
\todo[inline]{Idea: VPRO simulations using Cantera from a \ck{} file for an RCM
datapoint}
